### 2023-04-18 README.Rmd
fix an error in doc

`apptainerize()`/`singularize()` functions work exactly the same as `dockerize()`, expect you cannot cache Linux distribution rootfs.

@@

```bash
apptainer instance start \
    --enc RPORT=8080
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf,.rstudio:/home/rstudio/.rstudio/ \
    container.sif \
    rangtest
```

>>>>

`apptainerize()`/`singularize()` functions work exactly the same as `dockerize()`, except you cannot cache Linux distribution rootfs.

@@

```bash
apptainer instance start \
    --env RPORT=8080
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf,.rstudio:/home/rstudio/.rstudio/ \
    container.sif \
    rangtest
```
